$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/Referee-response.tex

\documentclass[12pt]{article}
\usepackage{fullpage}
\begin{document}
\noindent Dear editor,
\\

\noindent Thanks for sending us the referee responses. We would like to thank
the referee for their helpful comments and questions regarding our
paper. In response we have made changes to our manuscript and feel
these have improved the paper, we therefore hope our paper will now be
accepted for publication in PRD.
\\
\noindent We respond to each point raised by the referee below, explaining
where appropriate what we have done to address it in the paper.

\begin{itemize}
\item {\it ``in eq. (9) an additional parameter $\mu'$ appears.  Where
does it come from?  Even though it is later fixed to 5 TeV, it is not
clear if it has any impact on their study?  Even if it has no impact,
this should be stated somewhere.''}

The referee is correct to point out that the bilinear coupling $\mu'$ is
absent from the list of superpotential terms, and is lacking an explanation
in our original submission. The $\mu'$ term violates the $E_6$ symmetry, as
it is associated with the incomplete $27$ and $\overline{27}$ to which the
fields $\hat{H'}$ and $\hat{\overline{H}'}$ belong, but is invariant under
the Standard Model gauge group and the low energy $U(1)'$ symmetry. For this
reason it is not given in the superpotential in eq. (5). Additionally, because
this parameter does not appear in the EWSB conditions the impact from it on
the fine tuning can be neglected, and so fixing the value of $\mu'$ does not
impact the results.

To address this, we have added a short discussion immediately
following eq. (9) that explains the appearance of the additional parameter
and states that the chosen value of $\mu'$ does not impact on the fine
tuning in the study.

@@

\item {\it ``page 11: the authors state that they neglect gauge kinetic
mixing.  In view of possible effects on the LHC bounds: is this really
justified by the size of the off-diagonal entries in the anomalous
dimension matrix of the gauge fields?  This can be in particular important
because gauge kinetic mixing and additional decays in supersymmetric
particles affect the mass bound on a Z obtained from LHC and can lower them
by up to 200 GeV as has been discussed in arXiv:0909.1320, arXiv:1107.1133,
arXiv:1205.5780, arXiv:1206.3513 or their ref. 102.  How would such a shift
affect their conclusions?''}

This is an important point which we neglected to comment on in our
original article.  In the models we investigate numerically in our
paper, if gauge kinetic mixing is absent at the GUT scale it, the
radiatively induced gauge kinetic mixing will be rather small at the
EW scale as has been shown in the literature.  Therefore we neglected
this.  However the referee is correct that it is not the case in all
$U(1)$ extensions and this may have a significant impact on the
$Z^\prime$ mass limit.

To address this issue we have added remarks to the end of section III
explaining why it is small in the models we consider, with reference
to the previous literature and comment on how it will impact on tuning
results if one considers a case with large gauge kinetic mixing.

\item {\it ``page 13: the author state that the include leading
two-loop contributions to the Higgs mass.  Which are those?  Are the
corresponding contributions to the minimization equations 16 included
and, thus, in their measure of fine-tuning?  Concerning the two-loop part:
in eq. (9) the couplings $\kappa_i S D_i D_i$ are included.  As the extra
D-quarks have to be heavy, one would naively expect that they give a
sizable contribution to the Higgs masses at the 2-loop level, in particular
as they take in their numerical studies $|\lambda| \leq 3$.  Are those
included as well?''}

@@

The referee is correct that we missed the references specifying what
we mean by the leading two-loop corrections, so this was unclear.  We
included leading two-loop corrections calculated using effective field
theory methods, which have been generalised from well known
calculations in the MSSM and NMSSM.

To address this issue we have added references pointing out where we
obtained the leading two-loop Higgs corrections from.  For
completeness we also added a footnote pointing readers to the new tool
in the SARAH package which calculates the two-loop corrections to
Higgs masses in non-SUSY models.

We also understand why the referee may expect $\kappa$ couplings to give
a large contribution to the light Higgs mass, however we find that already
at one-loop the contribution from this coupling is small. The main reason
for this is the fact that singlet mixing with lightest Higgs is highly
suppressed in these models, which is a result of the large singlet VEV
required to meet the $Z^\prime$ limit.  The impact of the $\kappa$
couplings on the Higgs mass was also looked at in section 5.2.2 of
hep-ph/0510419.

The leading two-loop corrcetions to the effective potential are not
included in our calculation of the fine tuning.  Although the one-loop
effective potential corrections are important they are already smaller
than the RGE corrections and so we do not expect the two-loop
effective potential corrections to contribute at the same level as
the terms we include nor one which would significantly alter our
conclusions.

To address this we have added a comment specifying the precise one
loop corrections we use to the end of the paragraph below Eqn 30.

\item {\it ``on page 15 the authors claim that for $M_X = 10^{16}$ GeV a
lower bound of 200 for the fine tuning taking $m_h = 125$~GeV. Looking
at their approximation in the calculation of $m_h$ this mass has most
likely a theory uncertainty of about 10 GeV and, thus, I do not
understand how they can make such a statement.  This also concerns
their statement on page 17.''}

The referee is correct to point out that there is a large theoretical
uncertainty on the Higgs mass and we did not mean to suggest
otherwise.  When we discuss the fine tuning dependence on the Higgs
mass we are trying to show the qualitative behavior of the tuning
increasing with the Higgs mass and how this changes depending on the
UV cutoff.  We agree that the theoretical error on the Higgs mass is
rather large and that this affects the impact the Higgs mass
measurement has on the minimum tuning that is consistent with
observation.  However such discussions raise difficult questions about
how large the theoretical error is and how to address that in the context
of fine tuning.  Therefore we leave such tricky questions to papers
which are focussed on the impact on the Higgs rather than the fine
tuning from the $Z^\prime$ mass which we are interested in here.

To address the referee's remarks we have adjusted the wording of the
first comment referred to and have added a footnote pointing out that
there will be a sizable uncertainty of the Higgs mass.

\item {\it ``looking at their table II, one sees that in certain parts of
the parameter space, $A_t$ can be much larger than the corresponding soft
masses. This implies the danger of color and charge breaking minima as is
known for long time. I guess that quite some points are excluded by this.
Moreover, it seems that they allow also $|\mu|$ to be below 100 GeV which
would conflict LEP2 data. Are such points really included in their analysis?''}

\item {\it ``page 6: it is stated, that the $\hat N$ field remains
interactionless. However, to obtain light neutrino masses, there should be
at least Yukawa interactions.''}

The referee is correct to point out this out, and the sentence should instead
state that the $\hat N$ field does not participate in the gauge interactions
under the choice of $U(1)_N$. We have corrected this to address the referee's
comments.

\item {\it ``page 7: the $\hat N$ field is missing in equation 4''}

The referee's comment indicates that it was unclear the equation describes
only the low energy matter content in each $27$-plet, once the heavy fields
have been integrated out. The right-handed neutrinos are assumed to gain
large masses at some intermediate scale above the electroweak scale in order
to facilitate a see-saw mechanism for generating light neutrino masses.
Consequently they do not appear in the low energy matter content, so that
the equation is correct as currently written.

In order to address this and clarify the discussion, we have added a comment
immediately before the equation that explicitly mentions that the right-handed
neutrinos have been integrated out of the low energy theory.

\item {\it ``the journal is missing in ref. 57''}

This has been corrected by adding the journal title.

@@

\end{itemize}

In addition to the changes to address the referee's comments we also took the
opportunity to add two references we had missed out when we submitted the
article to PRD which are:
\begin{itemize}
\item [19]  M.~Drees, N.~K.~Falck and M.~Gluck, Phys.\ Lett.\ B {\bf 167},
187 (1986).
\item [46]  C.~Boehm, P.~S.~B.~Dev, A.~Mazumdar and E.~Pukartas, JHEP
{\bf 1306}, 113 (2013)
\end{itemize}

### 2015-05-15 paper/e6ssm-tuning-paper.tex
Fixed typos

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
Baer:2012up} with varying motivations.  A very different approach is
to work within a Bayesian analysis.  There the concept of naturalness
is automatically incorporated since in models where one must fine tune
parameters to fit measured values of the observables, the region with
high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the
VEVs, the inverse of the Jacobian for this transformation looks quite like
the derivatives that appear in the traditional fine tuning measure
\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
more generally then a model without fine tuning is one where the
parametrisation is such that all the parameters are observables
\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
the Jacobian for the co-ordinate transformation between the parameters
and the observables.  Interestingly this means the tuning is the ratio
of the infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real
VEVs of the form
\begin{equation} \label{eq:E6vevs}
\langle H_d \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} v_1 \\ 0
\end{pmatrix} , \;
\langle H_u \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} 0 \\ v_2
\end{pmatrix} , \;
\langle S \rangle =\frac{s}{\sqrt{2}} ,
\end{equation}
at the physical minimum leads to the minimization conditions
\begin{subequations} \label{eq:E6EWSBConditions}
\begin{align}
&f_1 = m_{H_d}^2 v_1 + \frac{\lambda^2}{2} (v_2^2 + s^2) v_1-
\frac{\lambda A_\lambda}{\sqrt{2}} s v_2 - \frac{\bar{g}^2}{8}
(v_2^2 - v_1^2) v_1 + D_{H_d} v_1 + \frac{\partial \Delta V}{\partial v_1} = 0 ,
\label{eq:E6EWSBcondition1} \\
&f_2 = m_{H_u}^2 v_2 + \frac{\lambda^2}{2} (v_1^2 + s^2) v_2 -
\frac{\lambda A_\lambda}{\sqrt{2}} s v_1 + \frac{\bar{g}^2}{8}
(v_2^2 - v_1^2) v_2 + D_{H_u} v_2 + \frac{\partial \Delta V}{\partial v_2} = 0 ,
\label{eq:E6EWSBcondition2} \\
&f_3 = m_S^2 s + \frac{\lambda^2}{2} (v_2^2 + v_1^2) s -
\frac{\lambda A_\lambda}{\sqrt{2}} v_2 v_1 + D_S s +
\frac{\partial \Delta V}{\partial s} = 0 . \label{eq:E6EWSBcondition3}
\end{align}
\end{subequations}
The quantities $D_{H_d}$, $D_{H_u}$ and $D_S$ appearing above are $U(1)'$
$D$-term contributions that are absent in the MSSM and NMSSM and are given by
\begin{equation} \label{eq:E6Dterms}
D_\phi \equiv \frac{g_1'^2}{2} \left (Q_1 v_1^2 + Q_2 v_2^2 + Q_S s^2
\right ) Q_\phi .
\end{equation}
We also include these $U(1)'$ $D$-term contributions in the diagonalised stop
masses,
\begin{align}
m_{\tilde{t}_{1,2}}^2 &= \frac{1}{2} \bigg \{ m_{Q_3}^2 + m_{u_3}^2 +
\frac{\bar{g}^2}{8} \left ( v_1^2 - v_2^2 \right ) + D_Q + D_u + 2 m_t^2
\nonumber \\
& \quad {} \mp \sqrt{\left [ m_{Q_3}^2 + m_{u_3}^2 + \frac{1}{8} \left (g_2^2
- g_1^2 \right ) \left (v_1^2 - v_2^2 \right ) + D_Q - D_u \right ]^2 +
4 m_t^2 X_t^2} \bigg \} ,
\end{align}
where $m_t^2 = y_t^2 v_2^2 / 2$, $X_t = A_t -
\frac{\lambda s v_1}{\sqrt{2} v_2}$, $m_{Q_3}^2$, $m_{u_3}^2$ are soft
breaking scalar masses and $A_t$ is a soft trilinear coupling.  By definition
we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.

@@

As stated above, to quantify the resulting fine tuning we apply the
traditional Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.
A specific model is characterised by a set of $n$ model parameters $\{p_i\}$
and is defined at some input scale $M_X$. For a given parameter $p$ in this
set, one computes an associated sensitivity
\begin{equation} \label{eq:bgmeasure}
\Delta_p = \left | \frac{\partial \ln M_Z^2}{\partial \ln p} \right
| = \left | \frac{p}{M_Z^2} \frac{\partial M_Z^2}{\partial p} \right | .
\end{equation}
The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$
resulting from a given variation in the parameter $p$.  The overall fine
tuning is then taken to be
$\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.\\

@@

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and for the light Higgs we
use the leading two-loop\footnote{Two-loop corrections calculated for
  a non-minimal SUSY model may now also be obtained from SARAH
  \cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not part
  of SARAH when we were doing the numerical work in this project and
  not currently used in FlexibleSUSY.  Such corrections go beyond the
  required precsion for studying fine tuning here.} contributions from \cite{King:2005jy} which
are a generalsiation of the correctsions in the MSSM and NMSSM
calculated using effective field theory techniques
\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
parameter space, the equivalent MSSM fine tuning expressions were
implemented into a modified version of SOFTSUSY 3.3.10
\cite{Allanach:2001kg}.  For consistency with the results produced in
the $E_6$ models, and for computational speed, for our main scans only
the dominant one- and two-loop corrections to the CP-even Higgs masses
were included.  Finally, in all of the results below the fine tuning
was evaluated at the scale $Q = M_{\textrm{SUSY}} =
\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
M_{\textrm{SUSY}}$.

@@

Since the stop mass does not have such a large impact on the fine
tuning when the cutoff scale is very low we can use this to see more
clearly the impact of the $Z^\prime$ mass on fine tuning.  To do so we
select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
between the MSSM and E$_6$SSM for two different values of the
$Z^\prime$ mass.  We choose to look at $M_{Z^\prime} = 2.5$ TeV, which is
just above the current limits, and $M_{Z^\prime} = 4.5$ TeV, which
should be in reach in run II at the LHC \cite{Godfrey:2013eta} and
then compare the fine tuning calculated in each case to the tuning in
the MSSM.  For this, we have performed a six dimensional parameter
space scan in both the MSSM and E$_6$SSM, varying those parameters
most relevant for the fine tuning and the Higgs mass.  Therefore the
set of parameters which we vary includes $\mu$, $B$ and $\tan\beta$
for the MSSM, and $\lambda$, $A_\lambda$ and $\tan\beta$, for the
E$_6$SSM, which appear at tree level in the EWSB conditions of the
models.  While the RGE contribution from large stop masses to the fine
tuning is small for such a low cutoff scale, the stop contributions to
the effective potential can play a significant role in reducing the
fine tuning.  For this reason it is still important to properly treat
the tuning associated with stop contributions to the one-loop
effective potential, and so we also scan over the soft masses
$m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.  The relevant
parameters and ranges that were scanned over are summarised in Table
\ref{tab:scanranges}.  In addition to this we also repeat each scan
for three different values of $M_2$ to allow more variation in the
chargino masses.

@@

Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
the E$_6$SSM looks more fine tuned than the MSSM this depends on the
high scale boundary, $M_X$, where the parameters are assumed to be set
by some SUSY breaking mechanism.  Indeed in \cite{Athron:2013ipa} a
constrained version of the E$_6$SSM, with the high scale boundary at
the GUT scale, is considered and there the cE$_6$SSM was found to be
less tuned than the cMSSM.  Since a 125 GeV Higgs can be achieved in
the E$_6$SSM with lighter stops, then if the cutoff is large, the
larger stop masses of the MSSM can make that model more fine tuned due
to large RGE effects.

@@

be GUT-normalised.  The expressions in terms of the $E_6$ mixing angle

>>>>

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
Baer:2012up} with varying motivations.  A very different approach is
to work within a Bayesian analysis.  There the concept of naturalness
is automatically incorporated since in models where one must fine tune
parameters to fit measured values of the observables, the region with
high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
the next-to-MSSM (NMSSM) if one transforms GUT scale parameters to the
VEVs, the inverse of the Jacobian for this transformation looks quite like
the derivatives that appear in the traditional fine tuning measure
\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
more generally then a model without fine tuning is one where the
parametrization is such that all the parameters are observables
\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
the Jacobian for the co-ordinate transformation between the parameters
and the observables.  Interestingly this means the tuning is the ratio
of the infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real
VEVs of the form
\begin{equation} \label{eq:E6vevs}
\langle H_d \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} v_1 \\ 0
\end{pmatrix} , \;
\langle H_u \rangle = \frac{1}{\sqrt{2}} \begin{pmatrix} 0 \\ v_2
\end{pmatrix} , \;
\langle S \rangle =\frac{s}{\sqrt{2}} ,
\end{equation}
at the physical minimum leads to the minimization conditions
\begin{subequations} \label{eq:E6EWSBConditions}
\begin{align}
&f_1 = m_{H_d}^2 v_1 + \frac{\lambda^2}{2} (v_2^2 + s^2) v_1-
\frac{\lambda A_\lambda}{\sqrt{2}} s v_2 - \frac{\bar{g}^2}{8}
(v_2^2 - v_1^2) v_1 + D_{H_d} v_1 + \frac{\partial \Delta V}{\partial v_1} = 0 ,
\label{eq:E6EWSBcondition1} \\
&f_2 = m_{H_u}^2 v_2 + \frac{\lambda^2}{2} (v_1^2 + s^2) v_2 -
\frac{\lambda A_\lambda}{\sqrt{2}} s v_1 + \frac{\bar{g}^2}{8}
(v_2^2 - v_1^2) v_2 + D_{H_u} v_2 + \frac{\partial \Delta V}{\partial v_2} = 0 ,
\label{eq:E6EWSBcondition2} \\
&f_3 = m_S^2 s + \frac{\lambda^2}{2} (v_2^2 + v_1^2) s -
\frac{\lambda A_\lambda}{\sqrt{2}} v_2 v_1 + D_S s +
\frac{\partial \Delta V}{\partial s} = 0 . \label{eq:E6EWSBcondition3}
\end{align}
\end{subequations}
The quantities $D_{H_d}$, $D_{H_u}$ and $D_S$ appearing above are $U(1)'$
$D$-term contributions that are absent in the MSSM and NMSSM and are given by
\begin{equation} \label{eq:E6Dterms}
D_\phi \equiv \frac{g_1'^2}{2} \left (Q_1 v_1^2 + Q_2 v_2^2 + Q_S s^2
\right ) Q_\phi .
\end{equation}
We also include these $U(1)'$ $D$-term contributions in the diagonalized stop
masses,
\begin{align}
m_{\tilde{t}_{1,2}}^2 &= \frac{1}{2} \bigg \{ m_{Q_3}^2 + m_{u_3}^2 +
\frac{\bar{g}^2}{8} \left ( v_1^2 - v_2^2 \right ) + D_Q + D_u + 2 m_t^2
\nonumber \\
& \quad {} \mp \sqrt{\left [ m_{Q_3}^2 + m_{u_3}^2 + \frac{1}{8} \left (g_2^2
- g_1^2 \right ) \left (v_1^2 - v_2^2 \right ) + D_Q - D_u \right ]^2 +
4 m_t^2 X_t^2} \bigg \} ,
\end{align}
where $m_t^2 = y_t^2 v_2^2 / 2$, $X_t = A_t -
\frac{\lambda s v_1}{\sqrt{2} v_2}$, $m_{Q_3}^2$, $m_{u_3}^2$ are soft
breaking scalar masses and $A_t$ is a soft trilinear coupling.  By definition
we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.

@@

As stated above, to quantify the resulting fine tuning we apply the
traditional Barbieri-Giudice measure \cite{Ellis:1986yg, Barbieri:1987fn}.
A specific model is characterized by a set of $n$ model parameters $\{p_i\}$
and is defined at some input scale $M_X$. For a given parameter $p$ in this
set, one computes an associated sensitivity
\begin{equation} \label{eq:bgmeasure}
\Delta_p = \left | \frac{\partial \ln M_Z^2}{\partial \ln p} \right
| = \left | \frac{p}{M_Z^2} \frac{\partial M_Z^2}{\partial p} \right | .
\end{equation}
The coefficient $\Delta_p$ measures the fractional variation in $M_Z^2$
resulting from a given variation in the parameter $p$.  The overall fine
tuning is then taken to be
$\Delta = \underset{i}{\max} \, \{ \Delta_{p_i} \}$.\\

@@

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and for the light Higgs we
use the leading two-loop\footnote{Two-loop corrections calculated for
a non-minimal SUSY model may now also be obtained from SARAH
\cite{Goodsell:2014pla,Goodsell:2015ira}.  However this was not part
of SARAH when we were doing the numerical work in this project and
not currently used in FlexibleSUSY.  Such corrections go beyond the
required precision for studying fine tuning here.} contributions from
\cite{King:2005jy} which are a generalization of the corrections in the
MSSM and NMSSM calculated using effective field theory techniques
\cite{Carena:1995wu, Ellwanger:1999ji}.  To scan over the MSSM
parameter space, the equivalent MSSM fine tuning expressions were
implemented into a modified version of SOFTSUSY 3.3.10
\cite{Allanach:2001kg}.  For consistency with the results produced in
the $E_6$ models, and for computational speed, for our main scans only
the dominant one- and two-loop corrections to the CP-even Higgs masses
were included.  Finally, in all of the results below the fine tuning
was evaluated at the scale $Q = M_{\textrm{SUSY}} =
\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
M_{\textrm{SUSY}}$.

@@

Since the stop mass does not have such a large impact on the fine
tuning when the cutoff scale is very low we can use this to see more
clearly the impact of the $Z^\prime$ mass on fine tuning.  To do so we
select a fixed low cutoff of $M_X=20$ TeV and compare the fine tuning
between the MSSM and E$_6$SSM for two different values of the
$Z^\prime$ mass.  We choose to look at $M_{Z^\prime} = 2.5$ TeV, which is
just above the current limits, and $M_{Z^\prime} = 4.5$ TeV, which
should be in reach in run II at the LHC \cite{Godfrey:2013eta} and
then compare the fine tuning calculated in each case to the tuning in
the MSSM.  For this, we have performed a six dimensional parameter
space scan in both the MSSM and E$_6$SSM, varying those parameters
most relevant for the fine tuning and the Higgs mass.  Therefore the
set of parameters which we vary includes $\mu$, $B$ and $\tan\beta$
for the MSSM, and $\lambda$, $A_\lambda$ and $\tan\beta$, for the
E$_6$SSM, which appear at tree level in the EWSB conditions of the
models.  While the RGE contribution from large stop masses to the fine
tuning is small for such a low cutoff scale, the stop contributions to
the effective potential can play a significant role in reducing the
fine tuning.  For this reason it is still important to properly treat
the tuning associated with stop contributions to the one-loop
effective potential, and so we also scan over the soft masses
$m_{Q_3}^2$, $m_{u_3}^2$ and the stop mixing $A_t$.  The relevant
parameters and ranges that were scanned over are summarized in Table
\ref{tab:scanranges}.  In addition to this we also repeat each scan
for three different values of $M_2$ to allow more variation in the
chargino masses.

@@

Finally we want to emphasize that while in Fig.~\ref{Fig:e6ssmvsmssm}
the E$_6$SSM looks more fine tuned than the MSSM this depends on the
high scale boundary, $M_X$, where the parameters are assumed to be set
by some SUSY breaking mechanism.  Indeed in \cite{Athron:2013ipa} a
constrained version of the E$_6$SSM, with the high scale boundary at
the GUT scale, is considered and there the cE$_6$SSM was found to be
less tuned than the cMSSM.  Since a 125 GeV Higgs can be achieved in
the E$_6$SSM with lighter stops, then if the cutoff is large, the
larger stop masses of the MSSM can make that model more fine tuned due
to large RGE effects.

@@

be GUT-normalized.  The expressions in terms of the $E_6$ mixing angle
